{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2025-08-17 lagrangian.tex
All sorts of crap from the last two years

Let us first look at the transformation of the superpotential $W$ under the gauge transformation of the scalar superfields in (\ref{eq:scalar_supergauge}):
\[W[\Phi] \to W[\Phi'] = g_i e^{iq_i\Lambda }\Phi_i + m_{ij}e^{i(q_i+q_j)\Lambda}\Phi_i\Phi_j + \lambda_{ijk}e^{i(q_i+q_j+q_k)\Lambda}\Phi_i\Phi_j\Phi_k.\]
Requiring gauge invariance, $W[\Phi] = W[\Phi']$, we must have:
\begin{eqnarray}
q_i &=& 0 ~~\text{or}~g_i = 0, \\
q_i+q_j &=& 0 ~~\text{or}~~m_{ij} = 0,  \\
q_i+q_j+q_k &=& 0  ~~\text{or}~~ \lambda_{ijk}=0.
\end{eqnarray}
This puts great restrictions on the form of the superpotential and the charge assignments of the superfields, as in ordinary gauge theories.

@@

For the superpotential to be gauge invariant we must now have:
\begin{eqnarray}
t_iU_{ir} &=& t_r ~~\text{or}~~ g_i = 0, \\
m_{ij}U_{ir} U_{js} &=& m_{rs} ~~\text{or}~~m_{ij}=0, \\
 \lambda_{ijk}U_{ir} U_{js}U_{kt}&=& \lambda_{rst} ~~\text{or}~~\lambda_{ijk}=0,
\end{eqnarray}
where the indices on $U$ are its matrix indices.

@@

The supergauge transformations of vector superfields can be written more efficiently in a representation independent way as
\[e^{V'} = e^{i\Lambda^\dagger}e^V e^{-i\Lambda},\]
where we have defined matrix superfields $\Lambda \equiv q \Lambda^aT_a$ and $V \equiv q V^aT_a$, and the inverse transformation is then given by
\[e^{-V'} = e^{i\Lambda}e^{-V} e^{-i\Lambda^\dagger},\]
such that $e^Ve^{-V} = e^{V'}e^{-V'} = 1$.\footnote{Notice that despite the non-commutative nature of the matrices involved, the identity $e^{A}e^{-A}=1$ holds. See Exercise~\ref{chap:groups}.\ref{ex:expmap_prop}.}

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{feynman}
%
\diagram [layered layout, horizontal=b to c] {
a [particle=$h$] -- [scalar] b [dot, black, label=$\lambda_f\hphantom{m}$]
-- [fermion, half left, out=90, in=90, edge label = $f$] c [dot, black, label=$\hphantom{nm}\lambda_f$]
-- [fermion, half left, out=90, in=90, edge label = $\bar{f}$] b,
c -- [scalar] d [particle=$h$],
};
%
\diagram [xshift=6cm, yshift=-0.6cm, layered layout, horizontal=b to c] {
a [particle=$h$] -- [scalar] b [dot, black,  label=$\lambda_s$]
-- [scalar] c [particle=$h$],
};
\path (b)--++(90:0.8) coordinate (A);
\path (b)--++(90:1.6) coordinate (B);
\draw [dashed] (A) circle(0.8);
\draw (B) node[above] {$s$};
%
%\diagram [xshift=10cm, layered layout, horizontal=b to c] {
%a [particle=$h$] -- [scalar] b [dot, black, label=$\lambda_V\hphantom{m}$]
%-- [boson, half left, out=90, in=90, edge label = $V$] c [dot, black, label=$\hphantom{nm}\lambda_V$]
%-- [boson, half left, out=90, in=90, edge label = $\bar{V}$] b,
%c -- [scalar] d [particle=$h$],
%};
%
\end{feynman}
\end{tikzpicture}
\caption{Higgs self-energy diagrams with fermions $f$ (left) and scalars $s$ (right). The dots indicate vertices with the given coupling strength.}  
\label{fig:hierarchy}
\end{figure}

There are different ways of achieving regularisation. Since we know that the Standard Model is an incomplete theory, at least when we go up to Planck scale energies where we need an unknown quantum theory of gravity, we can introduce a {\bf cut-off regularisation} where we limit the integral in the loop-correction to momenta below a scale $\Lambda_{UV}$. Then the loop-correction to the Higgs mass is, at leading order in $\Lambda_{UV}$,
\begin{equation}
\Delta m_h^2 = -\frac{|\lambda_f|^2}{8\pi^2}\Lambda_{UV}^2 + \frac{\lambda_s}{16\pi^2}\Lambda_{UV}^2+\ldots \label{eq:higgsqdiv}
\end{equation}
where $\lambda_f$ and $\lambda_s$ are the couplings of $f$ and $s$ to the Higgs, respectively, from the Lagrangian interaction terms $\mathcal L \sim \lambda_f \bar\psi\psi h+\text{h.c.}+\lambda_s |s|^2 |h|^2$. The dots represents terms that are less than quadratically divergent in terms of the cut-off scale, the first missing terms being logarithmically divergent.
Picking $\Lambda_{UV}$  suggestively as the Planck scale, $\Lambda_{UV} =M_P = 2.44\times 10^{18}$ GeV, meaning that the quantum corrections to the Higgs mass are some 15 orders of magnitude greater than its measured value.

@@

@@

>>>>

Let us first look at the transformation of the superpotential $W$ under the gauge transformation of the scalar superfields in (\ref{eq:scalar_supergauge}):
\[W[\Phi] \to W[\Phi'] = t_ie^{iq_i\Lambda }\Phi_i + m_{ij}e^{i(q_i+q_j)\Lambda}\Phi_i\Phi_j + \lambda_{ijk}e^{i(q_i+q_j+q_k)\Lambda}\Phi_i\Phi_j\Phi_k.\]
Requiring gauge invariance, $W[\Phi] = W[\Phi']$, we must have:
\begin{eqnarray}
q_i &=& 0 ~~\text{or}~t_i = 0, \\
q_i+q_j &=& 0 ~~\text{or}~~m_{ij} = 0,  \\
q_i+q_j+q_k &=& 0  ~~\text{or}~~ \lambda_{ijk}=0.
\end{eqnarray}
This puts great restrictions on the form of the superpotential and the charge assignments of the superfields, as in ordinary gauge theories.

@@

For the superpotential to be gauge invariant we must now have:
\begin{eqnarray}
t_iU_{ir} &=& t_r ~~\text{or}~~ t_i = 0, \\
m_{ij}U_{ir} U_{js} &=& m_{rs} ~~\text{or}~~m_{ij}=0, \\
 \lambda_{ijk}U_{ir} U_{js}U_{kt}&=& \lambda_{rst} ~~\text{or}~~\lambda_{ijk}=0,
\end{eqnarray}
where the indices on $U$ are its matrix indices.

@@

The supergauge transformations of vector superfields can be written more efficiently in a representation independent way as
\[e^{V'} = e^{i\Lambda^\dagger}e^V e^{-i\Lambda},\]
where we have defined matrix superfields $\Lambda \equiv q \Lambda^aT_a$ and $V \equiv q V^aT_a$, and the inverse transformation is then given by
\[e^{-V'} = e^{i\Lambda}e^{-V} e^{-i\Lambda^\dagger},\]
such that $e^Ve^{-V} = e^{V'}e^{-V'} = 1$.\footnote{Notice that despite the non-commutative nature of the matrices involved, the identity $e^{A}e^{-A}=1$ holds. See Exercise~\ref{chap:groups}.\ref{ex:expmapprop}.}

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{feynman}
%
\diagram [layered layout, horizontal=b to c] {
a [particle=$h$] -- [scalar] b [dot, black, label=$\lambda_f\hphantom{m}$]
-- [fermion, half left, out=90, in=90, edge label = $f$] c [dot, black, label=$\hphantom{nm}\lambda_f$]
-- [fermion, half left, out=90, in=90, edge label = $\bar{f}$] b,
c -- [scalar] d [particle=$h$],
};
%
\diagram [xshift=6cm, yshift=-0.6cm, layered layout, horizontal=b to c] {
a [particle=$h$] -- [scalar] b [dot, black,  label=$\lambda_s$]
-- [scalar] c [particle=$h$],
};
\path (b)--++(90:0.8) coordinate (A);
\path (b)--++(90:1.6) coordinate (B);
\draw [dashed] (A) circle(0.8);
\draw (B) node[above] {$s$};
%
\diagram [xshift=10cm, layered layout, horizontal=b to c] {
a [particle=$h$] -- [scalar] b [dot, black, label=$\lambda_V\hphantom{m}$]
-- [boson, half left, out=90, in=90, edge label = $V$] c [dot, black, label=$\hphantom{nm}\lambda_V$]
-- [boson, half left, out=90, in=90, edge label = $\bar{V}$] b,
c -- [scalar] d [particle=$h$],
};
%
\end{feynman}
\end{tikzpicture}
\caption{Higgs self-energy diagrams with fermions $f$ (left) and scalars $s$ (right). The dots indicate vertices with the given coupling strength.}  
\label{fig:hierarchy}
\end{figure}

There are different ways of achieving regularisation. Since we know that the Standard Model is an incomplete theory, at least when we go up to Planck scale energies where we need an unknown quantum theory of gravity, we can introduce a {\bf cut-off regularisation} where we limit the integral in the loop-correction to momenta below a scale $\Lambda$. Then the loop-corrections to the Higgs mass are
\begin{eqnarray}
\Delta m_{h,f}^2 &=& \frac{|\lambda_f|^2}{16\pi^2}\left[-2\Lambda^2 +6m_f^2\ln\frac{\Lambda}{m_f}+\ldots \right], \label{eq:higgsqdiv} \\
\Delta m_{h,s}^2 &=&  \frac{\lambda_s}{16\pi^2}\left[\Lambda^2 -2m_s^2\ln\frac{\Lambda}{m_s}+\ldots\right],  \\
\Delta m_{h,V}^2 &=& \frac{3\lambda_V^2}{16\pi^2}\left[\Lambda^2 - 2M_V^2\ln\frac{\Lambda}{M_V}+\ldots \right],
\end{eqnarray}
where $\lambda_f$, $\lambda_s$ and $\lambda_V$ are the couplings of $f$, $s$ and $V$ to the Higgs, respectively, from the Lagrangian interaction terms $\mathcal L \sim \lambda_f \bar\psi\psi h+\text{h.c.}-\frac{1}{4}\lambda_s |s|^2 |h|^2-\frac{1}{4}\lambda_V VV h$. The dots represents terms that are not divergent in terms of the cut-off scale.
Picking $\Lambda$  suggestively as the Planck scale, $\Lambda_{UV} =M_P = 2.44\times 10^{18}$ GeV, means that the quantum corrections to the Higgs mass are some 15 orders of magnitude greater than its measured value.

@@

There is a similar matching between the vector bosons and the fermions in the vector superfields.

@@

% Mention also that the prediction of the MSSM was < 150 geV while SM + X can give < 800 GeV, chance to exclude supersymmetry.

### 2025-08-17 notes.tex
All sorts of crap from the last two years

The goal of these lecture notes is to introduce the basics of low-energy models of supersymmetry (SUSY) using the Minimal Supersymmetric Standard Model (MSSM) as our main example. The notes are based on lectures given at the University of Oslo in 2011, 2013, 2015, 2017, 2019, 2021, and 2023, and lectures at the NORDITA Winter School on Theoretical Particle Physics in 2012.

Several student have contributed significantly to the notes. We owe a particular gratitude to Paul Batzing, who took notes during the 2011 lectures, forming the start of this document, and to Carl Martin Favang who fixed many mistakes. Morten Tryti Berg has supplied a solution to one of the exercises.

\vspace{5mm}
Oslo, October 2023

@@

From Chapter \ref{chap:mssm} and onwards we turn more towards phenomenology, constructing the minimal realisation of a supersymmetric Standard Model, before we discuss its phenomenology in Chapter \ref{chap:pheno}, before ending with a discussion of supersymmetric Dark Matter candidates in Chapter \ref{chap:dm}.

>>>>

The goal of these lecture notes is to introduce the basics of low-energy models of supersymmetry (SUSY) using the Minimal Supersymmetric Standard Model (MSSM) as our main example. The notes are based on lectures given at the University of Oslo in 2011, 2013, 2015, 2017, 2019, 2021, 2023, and 2025, and lectures at the NORDITA Winter School on Theoretical Particle Physics in 2012.

Several student have contributed significantly to these notes. We owe a particular gratitude to Paul Batzing, who took notes during the first version of the lectures in 2011, forming the start of this document, and to Carl Martin Favang who has fixed many of my mistakes. Morten Tryti Berg has supplied a solution to one of the exercises.

\vspace{5mm}
Oslo, October 2025

@@

From Chapter \ref{chap:mssm} and onwards we turn more towards phenomenology, constructing the minimal realisation of a supersymmetric Standard Model, before we discuss its phenomenology inChapter \ref{chap:pheno}, before ending with a discussion of supersymmetric Dark Matter candidates in Chapter \ref{chap:dm}.

### 2025-08-17 poincare.tex
All sorts of crap from the last two years

%%%%%%%%%%%%
\section{Weyl spinors}
\label{sec:weyl}
%%%%%%%%%%%%
As we discussed at the end of Sec.~\ref{sec:Lorentz_group} there exists a two-to-one homomorphism between the  $SL(2, \mathbb{C})$ and the Lorentz group $SO^+(1,3)$. This homomorphism, with $\Lambda^\mu{}_\nu \in SO^+(1,3)$ and $M \in SL(2, \mathbb{C})$, can be explicitly given by:\footnote{The choice of sign in Eq.~(\ref{eq:MofLambda}) is the reason that this is a homomorphism, instead of an isomorphism. Each element in  $SO^+(1,3)$ can be assigned to two in $SL(2, \mathbb{C})$.}
\begin{eqnarray}
\Lambda^\mu{}_\nu(M) &=& \frac{1}{2}{\rm Tr}[\bar{\sigma}^\mu M \sigma_\nu M^\dagger],\label{eq:LambdaofM}\\
M(\Lambda^\mu{}_\nu) &=& \pm \frac{1}{\sqrt{\det(\Lambda^\mu{}_\nu \sigma_\mu \bar{\sigma}^\nu)}}\Lambda^\mu{}_\nu \sigma_\mu \bar{\sigma}^\nu,\label{eq:MofLambda}
\end{eqnarray}
where $\bar{\sigma}^\mu = (1, -\vec{\sigma})$ and $\sigma^\mu = (1, \vec{\sigma})$. The generators of $SO^+(1,3)$ can be shown to transform to (be proportional to) the Pauli matrices in $SL(2,\mathbb C)$:
\[ J_i=\half \sigma_i, \quad K_i=\frac{i}{2}\sigma_i. \]

This two-to-one correspondence means that $SO^+(1,3) \cong SL(2, \mathbb{C})/\mathbb{Z}_2$ and the groups have the same algebra (as discussed in Sec.~\ref{sec:Lorentz_group} ). Thus we can look at the representations of $SL(2, \mathbb{C})$ instead of the  Lorentz group, when we describe spin-$\half$ particles,\footnote{We can of course also use the $SL(2, \mathbb{C})$ representations to construct representations for higher spin.} and working in $SL(2, \mathbb{C})$ if often much easier, but what are those representations? It turns out that there are two inequivalent fundamental representations $\rho$ of $SL(2, \mathbb{C})$ in terms of $2\times2$ matrices $M\in SL(2, \mathbb{C})$:
\begin{enumerate}[i)]
\item The self-representation $\rho(M) = M$  acting on a member $\psi$ of a representation vector space $V$:
\[\psi'_A = M_A{}^B\psi_B,  \quad A, B = 1,2.\]
\item The complex conjugate self-representation $\rho(M) = M^*$ working on a vector $\bar{\psi}$ in a space $\dot V$:
\[\bar{\psi}'_{\dot{A}} = (M^*)_{\dot{A}}{}^{\dot{B}}\bar{\psi}_{\dot{B}}, \quad  \dot{A}, \dot{B} = 1,2.\]
\end{enumerate}
The vectors $\psi$ and $\bar{\psi}$ in these representation spaces are called, respectively, {\bf left- and right-handed Weyl spinors}, and the induced representation of the Lorentz group is called the {\bf spinor representation}.
In addition to these two representations there are two dual representations, see Sec.~\ref{sec:dual_reps}, with $\rho(M)=M^{-1T}$ acting on vectors $\psi^A$ in $V^*$, and $\rho(M)=M^{*-1T}$ on vectors  $\bar\psi^{\dot{A}}$ in $\dot{V}^*$, that are equivalent to i) and ii), respectively.

The indices here follow the same summation rules as four-vectors. Indices can be lowered and raised with:
\begin{eqnarray}
\epsilon_{AB} &=& \epsilon_{\dot A \dot B} = \begin{pmatrix} 0 & -1\\ 1 & 0\end{pmatrix}, \label{eq:epsilonAB} \\
\epsilon^{AB} &=& \epsilon^{\dot{A}}{}^{\dot{B}} = \begin{pmatrix} 0 & 1\\ -1 & 0\end{pmatrix},\label{eq:epsilonAdotBdot}
\end{eqnarray}
which work as maps between the dual spaces.
The dots on the indices for the complex conjugate representation are there to help us remember which representation we are using and does not carry any additional importance, other than being a different index.

Since (\ref{eq:MofLambda}) gives $M$ in terms of the Pauli matrices, their index structure must be $\bar{\sigma^\mu}^{\dot{A}A}$ and $\sigma^\mu_{A\dot{A}}$. 
For a consistent index notation, the relationship between the vectors $\psi$ and $\bar{\psi}$ can be expressed with:
\[  \psi^A = \bar\psi_{\dot{A}}^*\bar{\sigma}^{0\dot{A}A}, \quad  \psi_A = {\sigma}^0_{A\dot{A}}\bar\psi^{\dot{A}*}, \quad  \bar{\psi}^{\dot{A}} = \bar{\sigma}^{0\dot{A}A}\psi_A^*, \quad \text{and}\quad  \bar{\psi}_{\dot{A}} =\psi^{A*} \sigma^0_{A\dot{A}} .\]
This may be seen as a bit of an overkill in indices as $\bar{\sigma^0}^{\dot{A}A} = \delta^{\dot{A}A}$, and we will in the following often omit the matrix and simply write $(\psi_A)^* = \bar{\psi}^{\dot{A}}$.
Note that from the above the following relationships hold for the hermitian conjugate:
\begin{eqnarray}
(\psi_A)^\dagger &=& \bar{\psi}_{\dot{A}} \\
(\bar{\psi}_{\dot{A}})^\dagger &=& \psi_A. \label{eq:Weyl_hc}
\end{eqnarray}

@@

%%%
\subsection{Useful relationships for Weyl spinors}
\label{sec:Weylspinor_calc}
%%%
For Weyl spinors $\psi$, $\eta$, and $\phi$ we can prove the following relationships\footnote{For clarity we have inserted parenthesis to show the different contractions.} 
\begin{eqnarray}
\eta\psi 				&=& \psi\eta,  \label{eq:Weylspinor_etapsi}  \\
\bar\eta\bar\psi 			&=& \bar\psi\bar\eta,  \\
(\eta\psi)^\dagger 		&=& \bar\psi\bar\eta,  \\
(\eta\psi)(\eta\phi) 		&=& -\frac{1}{2}(\eta\eta)(\psi\phi), \label{eq:Weylspinor_etapsietapsi}  \\
\eta\sigma^\mu\bar\psi 	&=& - \bar\psi\bar\sigma^\mu\eta,  \label{eq:Weylspinor_etasigmapsi} \\
(\sigma^\mu \bar{\eta})_A(\eta\sigma^\nu \bar{\eta})&=&\frac{1}{2}g^{\mu\nu}\eta_A(\bar{\eta}\bar{\eta}), \label{eq:Weylspinor_sigmaetaetasigmaeta}\\
(\eta\sigma^\mu \bar{\eta})(\eta\sigma^\nu \bar{\eta})&=&\frac{1}{2}g^{\mu\nu}(\eta\eta)(\bar{\eta}\bar{\eta}),   \label{eq:Weylspinor_etasigmamuetaetasigmanueta} \\
(\eta\sigma^\mu\partial_\mu \bar\psi )(\eta\psi) &=& -\frac{1}{2}(\psi\sigma^\mu\partial_\mu \bar\psi)(\eta\eta),\\
(\partial_\mu\psi\sigma^\mu \bar\eta)(\bar\eta\bar\psi) &=& -\frac{1}{2}(\partial_\mu\psi\sigma^\mu \bar\psi)(\bar\eta\bar\eta), \label{eq:Weylspinor_last} \\
\eta\sigma^{\mu\nu}\psi	&=&-\psi\sigma^{\mu\nu}\eta.   \label{eq:Weylspinor_etasigmamunupsi} 
\end{eqnarray}
Here $\sigma^{\mu\nu} = \frac{i}{4}(\sigma^\mu \bar{\sigma}^\nu - \sigma^\nu \bar{\sigma}^\mu)$.

@@

The equation of motion for spin-$\half$ particles with mass $m$ in relativistic quantum mechanics is the {\bf Dirac equation}
\begin{equation}
(i\slashed{\partial} -m)\psi=0,
\end{equation}
where the `slash' notation signifies contraction with a $\gamma$-matrix, $\slashed{\partial}\equiv\gamma^\mu\partial_\mu$, and where $\psi$ is a four component spinor constructed as above. Using Weyl spinors and the Weyl-representation of the $\gamma$-matrices this can be written as the coupled differential equations
\begin{eqnarray*}
i\sigma^\mu\partial_\mu\bar\chi -m\phi &=& 0,\\
i\bar\sigma^\mu\partial_\mu\phi -m\bar\psi &=& 0.
\end{eqnarray*}
In the massless limit or the extreme relativistic limit, $m\to 0$, these equations decouple into one separate equation per Weyl-spinor and become the {\bf Weyl-equations}
\begin{eqnarray*}
(i\partial_t - \boldsymbol\sigma\cdot \mathbf P) \bar\chi &=& 0,\\
(i\partial_t + \boldsymbol\sigma\cdot \mathbf P)\phi  &=& 0.
\end{eqnarray*}

@@

We should be a little careful about using the term particle about these states since what we have found for the fermions are in fact Weyl spinor states. From what we saw in Sec.~\ref{sec:weyl} a Dirac fermion can then only be described by a $j=0$ representation together with a different $j=0$ complex conjugate representation, thus consisting of four states.
The complex conjugate representation of the first representation together with the self-representation of the second then form the anti-particle of the fermion, and provide an additional two scalars. So the total particle count from the two irreducible representations is a fermion--anti-fermion pair, and four scalars. Note that all of the resulting particles have the same mass $m$.

>>>>

%%%%%%%%%%%%
\section{Weyl spinors}
\label{sec:weyl}
%%%%%%%%%%%%
As we discussed at the end of Sec.~\ref{sec:Lorentz_group} there exists a two-to-one homomorphism between the  $SL(2, \mathbb{C})$ and the Lorentz group $SO^+(1,3)$. This homomorphism, with $\Lambda^\mu{}_\nu \in SO^+(1,3)$ and $M \in SL(2, \mathbb{C})$, can be explicitly given by:\footnote{The choice of sign in Eq.~(\ref{eq:MofLambda}) is the reason that this is a homomorphism, instead of an isomorphism. Each element in  $SO^+(1,3)$ can be assigned to two elements in $SL(2, \mathbb{C})$.}
\begin{eqnarray}
\Lambda^\mu{}_\nu(M) &=& \frac{1}{2}{\rm Tr}[\bar{\sigma}^\mu M \sigma_\nu M^\dagger],\label{eq:LambdaofM}\\
M(\Lambda^\mu{}_\nu) &=& \pm \frac{1}{\sqrt{\det(\Lambda^\mu{}_\nu \sigma_\mu \bar{\sigma}^\nu)}}\Lambda^\mu{}_\nu \sigma_\mu \bar{\sigma}^\nu,\label{eq:MofLambda}
\end{eqnarray}
where $\bar{\sigma}^\mu = (1, -\vec{\sigma})$ and $\sigma^\mu = (1, \vec{\sigma})$. The generators of $SO^+(1,3)$ can be shown to transform to (be proportional to) the Pauli matrices in $SL(2,\mathbb C)$:
\[ J_i=\half \sigma_i, \quad K_i=\frac{i}{2}\sigma_i. \]

This two-to-one correspondence means that $SO^+(1,3) \cong SL(2, \mathbb{C})/\mathbb{Z}_2$ and the groups have the same algebra, as discussed in Sec.~\ref{sec:Lorentz_group}. Thus we can look at the representations of $SL(2, \mathbb{C})$ instead of the  Lorentz group, when we describe spin-$\half$ particles,\footnote{We can of course also use the $SL(2, \mathbb{C})$ representations to construct representations for higher spin.} and working in $SL(2, \mathbb{C})$ is often easier. But what are those representations? It turns out that there are two inequivalent fundamental representations $\rho$ of $SL(2, \mathbb{C})$ in terms of $2\times2$ matrices $M\in SL(2, \mathbb{C})$:
\begin{enumerate}[i)]
\item The self-representation $\rho(M) = M$  acting on a member $\psi$ of a representation vector space $V$:
\[\psi'_A = M_A{}^B\psi_B,  \quad A, B = 1,2.\]
\item The complex conjugate self-representation $\rho(M) = M^*$ working on a vector $\bar{\psi}$ in a space $\dot V$:
\[\bar{\psi}'_{\dot{A}} = (M^*)_{\dot{A}}{}^{\dot{B}}\bar{\psi}_{\dot{B}}, \quad  \dot{A}, \dot{B} = 1,2.\]
\end{enumerate}
The indices here follow the same summation conventions as four-vectors. 
The vectors $\psi$ and $\bar{\psi}$ in these representation spaces are called, respectively, {\bf left- and right-handed Weyl spinors}, and the representation of the Lorentz group induced by the homomorphism is called the {\bf spinor representation}.
In addition to these two representations there are two dual representations, see Sec.~\ref{sec:dual_reps}, with $\rho(M)=M^{-1T}$ acting on vectors $\psi^A$ in $V^*$, the dual space of $V$, and $\rho(M)=M^{*-1T}$ acting on vectors  $\bar\psi^{\dot{A}}$ in $\dot{V}^*$, that are equivalent to i) and ii), respectively.

Indices can be lowered and raised with:
\begin{eqnarray}
\epsilon_{AB} &=& \epsilon_{\dot A \dot B} = \begin{pmatrix} 0 & -1\\ 1 & 0\end{pmatrix}, \label{eq:epsilonAB} \\
\epsilon^{AB} &=& \epsilon^{\dot{A}}{}^{\dot{B}} = \begin{pmatrix} 0 & 1\\ -1 & 0\end{pmatrix},\label{eq:epsilonAdotBdot}
\end{eqnarray}
which work as maps between the dual spaces.
The dots on the indices for the complex conjugate representation are there to help us remember which representation we are using and does not carry any additional importance, other than being a different index.

Since (\ref{eq:MofLambda}) gives $M$ in terms of the Pauli matrices, their index structure must be $\bar{\sigma^\mu}^{\dot{A}A}$ and $\sigma^\mu_{A\dot{A}}$. 
For a consistent index notation, the relationship between the vectors $\psi$ and $\bar{\psi}$ can be expressed with:
\[  \psi^A = \bar\psi_{\dot{A}}^*\bar{\sigma}^{0\dot{A}A}, \quad  \psi_A = {\sigma}^0_{A\dot{A}}\bar\psi^{\dot{A}*}, \quad  \bar{\psi}^{\dot{A}} = \bar{\sigma}^{0\dot{A}A}\psi_A^*, \quad \text{and}\quad  \bar{\psi}_{\dot{A}} =\psi^{A*} \sigma^0_{A\dot{A}} .\]
This may seem as a bit of an overkill in indices as the sigma matrices involved are the identity: $\bar{\sigma}^{0\dot{A}A} = \delta^{\dot{A}A}$ and  $\sigma^0_{A\dot{A}} = \delta_{A\dot{A}}$, and we will in the following often omit the $\sigma^0$ matrix and simply write $(\psi_A)^* = \bar{\psi}^{\dot{A}}$ and similarly.
Note that from the above the following relationships hold for the hermitian conjugate when we ignore the $\sigma^0$ matrices that keep track of the indices:
\begin{eqnarray}
(\psi_A)^\dagger &=& \bar{\psi}_{\dot{A}} \\
(\bar{\psi}_{\dot{A}})^\dagger &=& \psi_A. \label{eq:Weyl_hc}
\end{eqnarray}

@@

%%%
\subsection{Useful relationships for Weyl spinors}
\label{sec:Weylspinor_calc}
%%%
For Weyl spinors $\psi$, $\eta$, and $\phi$ we can prove the following relationships\footnote{For clarity we have inserted parenthesis to show the different contractions.} 
\begin{eqnarray}
\eta\psi 				&=& \psi\eta,  \label{eq:Weylspinor_etapsi}  \\
\bar\eta\bar\psi 			&=& \bar\psi\bar\eta, \label{eq:Weylspinor_contraction_order_bared} \\
(\eta\psi)^\dagger 		&=& \bar\psi\bar\eta,  \\
(\eta\psi)(\eta\phi) 		&=& -\frac{1}{2}(\eta\eta)(\psi\phi), \label{eq:Weylspinor_etapsietapsi}  \\
\eta\sigma^\mu\bar\psi 	&=& - \bar\psi\bar\sigma^\mu\eta,  \label{eq:Weylspinor_etasigmapsi} \\
(\sigma^\mu \bar{\eta})_A(\eta\sigma^\nu \bar{\eta})&=&\frac{1}{2}g^{\mu\nu}\eta_A(\bar{\eta}\bar{\eta}), \label{eq:Weylspinor_sigmaetaetasigmaeta}\\
(\eta\sigma^\mu \bar{\eta})(\eta\sigma^\nu \bar{\eta})&=&\frac{1}{2}g^{\mu\nu}(\eta\eta)(\bar{\eta}\bar{\eta}),   \label{eq:Weylspinor_etasigmamuetaetasigmanueta} \\
(\eta\sigma^\mu\partial_\mu \bar\psi )(\eta\psi) &=& -\frac{1}{2}(\psi\sigma^\mu\partial_\mu \bar\psi)(\eta\eta),\\
(\partial_\mu\psi\sigma^\mu \bar\eta)(\bar\eta\bar\psi) &=& -\frac{1}{2}(\partial_\mu\psi\sigma^\mu \bar\psi)(\bar\eta\bar\eta), \label{eq:Weylspinor_last} \\
\eta\sigma^{\mu\nu}\psi	&=&-\psi\sigma^{\mu\nu}\eta.   \label{eq:Weylspinor_etasigmamunupsi} 
\end{eqnarray}
Here $\sigma^{\mu\nu} = \frac{i}{4}(\sigma^\mu \bar{\sigma}^\nu - \sigma^\nu \bar{\sigma}^\mu)$.

@@

We define a bared version of the Dirac spinor by  $\bar\psi \equiv \psi^\dagger\gamma^0$, which can be written in terms of Weyl spinors as 
\begin{equation*}
\bar\psi  =\begin{pmatrix}\phi_A^\dagger & \bar{\chi}^{\dot{A}^\dagger}\end{pmatrix} \left(\begin{matrix} 0 & \sigma^0_{A\dot{A}} \\ \bar\sigma^{0\dot A A} & 0 \end{matrix}\right)
= \begin{pmatrix}  \bar{\chi}^{\dot{A}*}\bar\sigma^{0\dot A A}  & \phi_A^*  \sigma^0_{A\dot{A}} \end{pmatrix}
= \begin{pmatrix}  \chi^A & \bar{\phi}_{\dot A} \end{pmatrix}.
\end{equation*}

%%%
\subsection{Dirac and Weyl equations}
\label{sec:fermion_eoms}
%%%

The equation of motion for spin-$\half$ particles with mass $m$ can be found from the Dirac Lagrangian written in terms of the  four component spinor constructed above,
\begin{equation}
\mathcal L_D = \bar\psi (i \slashed{\partial}-m)\psi,
\label{eq:Dirac_lagrangian}
\end{equation}
where the `slash' notation signifies contraction with a $\gamma$-matrix, $\slashed{\partial}\equiv\gamma^\mu\partial_\mu$, and where an identity matrix is implied for the mass term. After solving for $\psi$ using the Lagrange equation this gives the {\bf Dirac equation} of motion
\begin{equation}
(i\slashed{\partial} -m)\psi=0.
\end{equation}

In two-component Weyl-spinor notation, using the Weyl-representation og the $\gamma$-matrices, the Lagrangian (\ref{eq:Dirac_lagrangian}) becomes
\begin{eqnarray*}
\mathcal L_D &=& \begin{pmatrix}  \chi^A & \bar{\phi}_{\dot A} \end{pmatrix} \left(\begin{matrix} -m  & i\sigma^\mu_{A\dot A}\partial_\mu \\  i\bar\sigma^{\mu\dot A A}\partial_\mu& -m \end{matrix}\right) \begin{pmatrix}\phi_A\\ \bar{\chi}^{\dot{A}}\end{pmatrix} \\
&=& -m  \chi \phi + i\chi\sigma^\mu\partial_\mu\bar\chi+ i\bar\phi\bar\sigma^\mu\partial_\mu\phi -m\bar\phi\bar\chi \\
&=& i\chi\sigma^\mu\partial_\mu\bar\chi+ i\bar\phi\bar\sigma^\mu\partial_\mu\phi  -m  (\chi \phi + \bar\phi\bar\chi).  
\end{eqnarray*}
Here we can use (\ref{eq:Weylspinor_contraction_order_bared}) and (\ref{eq:Weylspinor_etasigmapsi}) with
\begin{equation}
i\chi\sigma^\mu\partial_\mu\bar\chi = \partial_\mu (i\chi\sigma^\mu\bar\chi) - i\partial_\mu\chi\sigma^\mu\bar\chi =  i\bar\chi\bar\sigma^\mu\partial_\mu\chi,
\end{equation}
where we assume the surface term disappears, to make the expression more symmetric
\begin{equation*}
\mathcal L_D = i\bar\chi\bar\sigma^\mu\partial_\mu\chi+ i\bar\phi\bar\sigma^\mu\partial_\mu\phi  -m  (\chi \phi + \bar\chi\bar\phi).  
\end{equation*}

The equation of motion for the Weyl-spinors that corresponds to the Dirac equation can be found by using the Lagrange equation for $\chi$ and $\bar\phi$
 as the coupled differential equations
\begin{eqnarray*}
i\sigma^\mu\partial_\mu\bar\chi -m\phi &=& 0,\\
i\bar\sigma^\mu\partial_\mu\phi -m\bar\chi &=& 0.
\end{eqnarray*}
In the massless limit or the extreme relativistic limit, $m\to 0$, these equations decouple into one separate equation per Weyl-spinor and become the {\bf Weyl-equations}
\begin{eqnarray*}
(i\partial_t - \boldsymbol\sigma\cdot \mathbf P) \bar\chi &=& 0,\\
(i\partial_t + \boldsymbol\sigma\cdot \mathbf P)\phi  &=& 0.
\end{eqnarray*}

@@

We should use be a little careful about using the term particle about these states since what we have found for the fermions are in fact Weyl spinor states. From what we saw in Sec.~\ref{sec:weyl} a Dirac fermion can then only be described by a $j=0$ representation together with a different $j=0$ complex conjugate representation, thus consisting of four states.
The complex conjugate representation of the first representation together with the self-representation of the second then form the anti-particle of the fermion, and provide an additional two scalars. So the total particle count from the two irreducible representations is a fermion--anti-fermion pair, and four scalars. Note that all of the resulting particles have the same mass $m$.
